Verification of Stencil Computations with Spatial Specifications

### 2016-11-11 paper.tex
on an informal definition of consistency

\begin{definition}[Consistency, informal]
  A stencil specification defines a \emph{region} which, informally,
  is an n-dimensional rectangle which is possibly infinite in some
  dimensions. A stencil kernel in code is \emph{consistent} with a
  specification on array variable $a$ if every array index on $a$
\end{definition}

>>>>

\begin{definition}[Consistency, informal]
  A stencil specification defines a \emph{region} which, informally,
  is an n-dimensional rectangle which is possibly infinite in some
  dimensions. A stencil kernel in code is \emph{consistent} with a
  specification on array variable $a$ if every array index on $a$
  is a neighbourhood index within the $n$-dimensional rectangle
  specified by the 
\end{definition}
